The illusory promise of the Aligned Rank Transform

### 2025-05-24 supplementary/examples-case-studies/1-Introduction/illustrative-example.Rmd
updated repository from jovi

We read our dataset and fix the type of the factors:
```{r, warning=FALSE}
df <- read.csv("example-data-cut.csv", sep=",", header=TRUE, strip.white=TRUE)

>>>>

We read our dataset and fix the type of the factors:
```{r, warning=FALSE}
df <- read.csv("example-data.csv", sep=",", header=TRUE, strip.white=TRUE)

### 2025-05-24 supplementary/rebuttals/higgins/homoscedastic/example/additional-example.Rmd
updated repository from jovi

---
title: "Introduction - Illustrative example"
author: "Theophanis Tsandilas and Géry Casiez"
output: html_document
---

@@

We detail our analysis for the illustrative example presented in the Introduction.

We use [data](example-data-2.csv) from a hypothetical experiment that evaluates the time performance of three user interface techniques (*A*, *B*, and *C*) that help users complete image editing tasks of four different difficulty levels: *Level1*, *Level2*, *Level3*, and *Level4*.

>>>>

---
title: "Rebuttal - Complimentary example (homoscedastic log-normal data)"
author: "Theophanis Tsandilas and Géry Casiez"
output: html_document
---

@@

We detail the analysis for a complimentary example where data were drawn from homoscedastic log-normal populations. We present this example in our [first answer](https://github.com/journalovi/2024-tsandilas-ranktransforms/issues/2#issuecomment-2483020115) to the commentary of Prof. James Higgins.

As in our original illustrative example, we use [data](example-data-2.csv) from a hypothetical experiment that evaluates the time performance of three user interface techniques (*A*, *B*, and *C*) that help users complete image editing tasks of four different difficulty levels: *Level1*, *Level2*, *Level3*, and *Level4*.

### 2025-05-24 text/20-intro.qmd
updated repository from jovi

The experiment is hypothetical but has similarities with real-world experiments, e.g., see the experiments of @Fruchard:2023. Time performances have been randomly sampled from a population in which: (1) *Difficulty* has a large effect; (2) *Technique* has no effect; and (3) there is no interaction effect between the two factors. To generate time values, we drew samples from a log-normal distribution. The log-normal distribution is often a good fit for real-world measurements that are bounded by zero and have low means but large variance [@Limbert:2001]. Task-completion times are good examples of such measurements [@Sauro:2010].

>>>>

The experiment is hypothetical but has similarities with real-world experiments, e.g., see the experiments of @Fruchard:2023. Time performances have been randomly sampled from a population in which: (1) *Difficulty* has a large main effect; (2) *Technique* has no main effect; and (3) there is no interaction effect between the two factors. To generate time values, we drew samples from a log-normal distribution. The log-normal distribution is often a good fit for real-world measurements that are bounded by zero and have low means but large variance [@Limbert:2001]. Task-completion times are good examples of such measurements [@Sauro:2010].
